---
title: cori.data.fcc
description: Functions to get and process FCC data
author: Olivier Leroy
date: '2026-05-05'
categories:
  - R Package
  - Broadband
tags:
  - broadband
  - fcc
  - nbm
  - national-broadband-map
  - form-477
  - census-block
  - isp
package:
  name: cori.data.fcc
  githubUrl: https://github.com/ruralinnovation/cori.data.fcc
  installCommand: devtools::install_github("ruralinnovation/cori.data.fcc")
  status: stable
  version: 1.0.0
  maintainer: Olivier Leroy
  featured: false
usesDatasets:
  - fcc-broadband
usesResources: []
execute:
  echo: true
  warning: false
  message: false
editor:
  markdown:
    wrap: 72
---

## Overview

The goal of cori.data.fcc is to facilitate the discovery, analysis, and use of FCC public data releases. The package provides S3-backed access to National Broadband Map (NBM) data — both raw parquet files by county and a CORI-opinionated Census-block-level summary — as well as Form 477 broadband deployment data spanning multiple years. A built-in data dictionary and ISP provider reference table round out the package.

::: callout-note
## Why Use This Package

- **S3-backed NBM access via DuckDB** - Raw NBM parquet files queryable by county without local download, powered by DuckDB
- **CORI-opinionated block layer** - 21-column Census-block summary with technology type breakdowns (fiber, cable, copper, fixed wireless, etc.) and BEAD location counts
- **FRN-based coverage queries** - Retrieve all Census blocks served by a specific ISP using their FCC Registration Number
- **Form 477 multi-year data** - State-level broadband deployment records from 2014 onward
- **Integrated data dictionary** - 50-row codebook covering f477, nbm_block, and nbm_raw field descriptions
- **ISP provider reference** - fcc_provider data frame with 4,456 records linking provider names, FRNs, and numeric provider IDs
:::

## Installation

```{r}
#| eval: false

devtools::install_github("ruralinnovation/cori.data.fcc")
```

## Quick Start

```{r}
#| eval: false

library(cori.data.fcc)

# Get CORI-opinionated NBM block-level data for a county
nbm_bl <- get_nbm_bl(geoid_co = "47051")

# Get raw NBM parquet data for a county
guilford_cty <- get_nbm_county_raw(geoid_co = "37081")

# Get all blocks served by a specific ISP (by FRN)
skymesh <- get_frn_nbm_bl("0027136753")

# Get Form 477 data for a state
f477_vt <- get_f477("VT")
```

## Core Functions

::: panel-tabset

### Data Access

| Function | Description |
|----------|-------------|
| `get_nbm_bl()` | CORI-opinionated NBM Census-block summary by county (21 columns) |
| `get_nbm_county()` | NBM county-level aggregated data |
| `get_nbm_county_raw()` | Raw NBM parquet data for a county and release via S3 |
| `get_frn_nbm_bl()` | All Census blocks where a given FRN reported service |
| `get_f477()` | Form 477 broadband deployment data by state |

### Utility

| Function | Description |
|----------|-------------|
| `get_nbm_available()` | List available NBM releases in the S3 store |
| `get_nbm_release()` | NBM release metadata |
| `dl_nbm()` | Download NBM source files |
| `check_frn()` | Validate an FCC Registration Number (FRN) |
| `get_fcc_dictionary()` | 50-row codebook across all package datasets |

:::

## Data Sources

| Dataset | Role |
|---------|------|
| [FCC Broadband](/datasets/fcc-broadband/) | Primary |

## Use Cases at CORI

This package is used in:

- Analyzing broadband availability at the Census-block level for a county or region
- Identifying BEAD-eligible locations using CORI-processed NBM data
- Querying coverage footprint for a specific ISP by FRN
- Tracking broadband deployment trends over time using Form 477 filings
- Building broadband gap analyses using technology-type breakdowns

::: callout-tip
## Optimization Tips

Ensure the latest versions of duckdb and waldo are installed before use. The raw NBM data (parquet via S3) can be large — queries against get_nbm_county_raw() on dense counties may return over one million rows.
:::

::: callout-warning
## Known Limitations

The package accesses data stored in CORI S3 storage; AWS credentials or network access may be required. NBM data reflects ISP-reported coverage and is subject to the known limitations of self-reported broadband availability data.
:::

## Documentation

- [GitHub Repository](https://github.com/ruralinnovation/cori.data.fcc)
- [Full README](https://github.com/ruralinnovation/cori.data.fcc/blob/main/README.md)
- [Function Documentation](https://github.com/ruralinnovation/cori.data.fcc/tree/main/man)

