---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cori.data.fcc

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/ruralinnovation/cori.data.fcc/branch/main/graph/badge.svg)](https://app.codecov.io/gh/ruralinnovation/cori.data.fcc?branch=main)
[![R-CMD-check](https://github.com/ruralinnovation/cori.data.fcc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ruralinnovation/cori.data.fcc/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `cori.data.fcc` is to facilitate the discovery, analysis, and use of FCC public data releases.

The package provides access to data from the following sources:

  -  National Broadband Map [(NBM)](https://broadbandmap.fcc.gov/home) data[^bdc]
  -  [Form 477](https://www.fcc.gov/general/broadband-deployment-data-fcc-form-477) data

[^bdc]: This data describes what internet services are available to individual locations across the country, along with new maps of mobile coverage, as reported by Internet Service Providers (ISPs). It is part of the FCC’s ongoing [Broadband Data Collection](https://broadbandmap.fcc.gov/data-download/nationwide-data)).

## Installation

You can install the development version of `cori.data.fcc` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ruralinnovation/cori.data.fcc")
```

## Examples

```{r load}
library(cori.data.fcc)
```

### National Broadband Map

Key uses:

- Access parquet files stored in a CORI s3 bucket, by county:

```{r nbm_raw}
guilford_cty <- get_county_nbm_raw(geoid_co = "37081")
dplyr::glimpse(guilford_cty)
```

- Access a CORI-opinionated, Census-block level version of the **latest NBM release**:

```{r nbm_block}
# get a county
nbm_bl <- get_nbm_bl(geoid_co = "47051")
dplyr::glimpse(nbm_bl)

# get census block covered by an ISP identified by their FRN
skymesh <- get_frn_nbm_bl("0027136753")
dplyr::glimpse(skymesh)

```

### Form 477

Access state data for multiple years:

```{r get_f477_example}
f477_vt <- get_f477("VT")
dplyr::glimpse(f477_vt)
```

### Utilities

Access the dictionary for each dataset:

```{r get_fcc_dictionary_ex}
dplyr::glimpse(get_fcc_dictionary())
```


The package also provides a list of Provider IDs and FRNs.

```{r fcc_provider}
str(fcc_provider)
```

## Inspiration

This package was inspired by https://github.com/bbcommons/bfm-explorer 
