---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cori.data.fcc

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/ruralinnovation/cori.data.fcc/branch/main/graph/badge.svg)](https://app.codecov.io/gh/ruralinnovation/cori.data.fcc?branch=main)
[![R-CMD-check](https://github.com/ruralinnovation/cori.data.fcc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ruralinnovation/cori.data.fcc/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `cori.data.fcc` is to facilitate the discovery, analysis, and use of FCC public data releases.

The package provides access to data from the following sources:

  -  National Broadband Map [(NBM)](https://broadbandmap.fcc.gov/home) data[^bdc]
  -  [Form 477](https://www.fcc.gov/general/broadband-deployment-data-fcc-form-477) data

[^bdc]: This data describes what internet services are available to individual locations across the country, along with new maps of mobile coverage, as reported by Internet Service Providers (ISPs). It is part of the FCC’s ongoing [Broadband Data Collection](https://broadbandmap.fcc.gov/data-download/nationwide-data)).

## Installation

You can install the development version of `cori.data.fcc` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ruralinnovation/cori.data.fcc")
```

## Examples

```{r load}
library(cori.data.fcc)
```

### National Broadband Map

Key uses:

- Access parquet files stored in a CORI s3 bucket, by county:

```{r nbm_raw}
guilford_cty <- get_nbm_county_raw(geoid_co = "37081")
dplyr::glimpse(guilford_cty)
```

- Access a CORI-opinionated, Census-block level version of the **latest NBM release**:

```{r nbm_block}
# get a county
nbm_bl <- get_nbm_bl(geoid_co = "47051")
dplyr::glimpse(nbm_bl)

# get census block covered by an ISP identified by their FRN
skymesh <- get_frn_nbm_bl("0027136753")
dplyr::glimpse(skymesh)

```

### Form 477

Access state data for multiple years:

```{r get_f477_example}
f477_vt <- get_f477("VT")
dplyr::glimpse(f477_vt)
```

### Utilities

Access the dictionary for each dataset:

```{r get_fcc_dictionary_ex}
dplyr::glimpse(get_fcc_dictionary())
```


The package also provides a list of Provider IDs and FRNs.

```{r fcc_provider}
str(fcc_provider)
```

## Incorporating the BDC Public Data API

The FCC's National Broadband Map exposes a public REST API (documented at
https://us-fcc.app.box.com/v/bdc-public-data-api-swagger) that offers a more
structured alternative to the bulk download workflow currently implemented in
`data-raw/`. Three endpoints are directly relevant to the ingestion pipeline.

`GET /api/public/map/listAsOfDates` returns every available release date for
both availability and challenge data types. This is a programmatic replacement
for `get_nbm_release()`, which currently scrapes a separate filing endpoint.

`GET /api/public/map/downloads/listAvailabilityData/{as_of_date}` returns a
full manifest for a given release — including a stable numeric `file_id`,
`file_name`, `record_count`, `state_fips`, `provider_id`, and category
metadata for every downloadable file. This replaces `get_nbm_available()` and,
crucially, provides the information currently reconstructed by hand from
inconsistent FCC filename patterns (the 100-line normalization block in
`data-raw/nbm_raw.R` that repairs `December20ec_`, `June20un_`, and
abbreviated date codes like `D22`/`J23`).

`GET /api/public/map/downloads/downloadFile/availability/{file_id}/1` downloads
a file by its stable numeric ID rather than by a constructed URL. Combined with
the manifest's `as_of_date` field, the release date embedded in the DuckDB
`strptime(split_part(filename, '_', 7), '%B%Y')` expression could simply be
passed in directly, eliminating all filename-based date parsing.

The manifest's `record_count` field also enables a more meaningful post-download
validation than the current file-presence check: row counts loaded into DuckDB
can be compared against the API's declared counts before committing a partition.
Because the manifest is date-scoped, comparing it against already-ingested
parquet partitions makes incremental ingestion (downloading only new releases)
straightforward to implement.

All API endpoints require a `username` and `hash_value` request header. The
token is generated once via the NBM web interface at
https://broadbandmap.fcc.gov/login under Manage API Access, and the recommended
approach for storing it in R is `keyring`. The `fcc_provider` table (currently
fetched from a hardcoded Box URL in `data-raw/fcc_provider.R`) is not exposed
through the BDC API and would remain unchanged.

## Inspiration

This package was inspired by https://github.com/bbcommons/bfm-explorer

## DuckDB httpfs Configuration — Changelog and Notes

### Background: SSL error with dot-named S3 buckets

In late 2025, the `duckdb` R package began producing SSL certificate errors when
reading parquet files from S3 buckets whose names contain dots (e.g.,
`cori.data.bds`). The root cause is a hostname mismatch: AWS's virtual-hosted
URL style turns `cori.data.bds` into the subdomain
`cori.data.bds.s3.us-east-1.amazonaws.com`, which has too many labels for
AWS's wildcard TLS certificate (`*.s3.us-east-1.amazonaws.com` covers only
one subdomain level). The error surfaced as:

```
SSL peer certificate or SSH remote key was not OK error for HTTP GET to
'https://cori.data.bds.s3.us-east-1.amazonaws.com/...'
```

The fix is one DuckDB setting that switches URL construction from
virtual-hosted style to path style, routing requests as
`https://s3.us-east-1.amazonaws.com/<bucket>/...` instead:

```r
DBI::dbExecute(con, "SET s3_url_style = 'path';")
```

Although `cori.data.fcc` (no dots in the bucket name) was not directly
affected by this SSL error, the same setting was applied across all functions
in this package for consistency with the rest of the coriverse.

### Background: HTTP timeout failures in DuckDB 1.4.4+

After applying the SSL fix, a new class of errors appeared in the test suite
for functions that query S3 directly via DuckDB's httpfs extension (primarily
`get_frn_nbm_bl`, which scans all state-level parquet partitions to find rows
matching a given FRN):

```
IO Error: Timeout was reached error for HTTP GET to
'https://s3.us-east-1.amazonaws.com/cori.data.fcc/nbm_block-J24/state_abbr=AR/data_0.parquet'
```

The `http_timeout` setting defaults to 30 seconds and applies per HTTP
request, not per query. Reading a single large state parquet file from S3
requires multiple HTTP range requests (footer metadata, then individual row
groups), and with DuckDB 1.4.4 the behaviour of the built-in `httplib` HTTP
client changed in ways that increased per-request latency — particularly
documented in duckdb/duckdb-java#548
(https://github.com/duckdb/duckdb-java/issues/548). Additionally,
`httpfs_connection_caching` defaults to `false`, meaning every range request
opens a fresh TCP + TLS connection to `s3.us-east-1.amazonaws.com` rather
than reusing an already-negotiated session.

### Changes applied to all httpfs connections in this package

Three settings are now explicitly configured on every DuckDB connection that
uses the httpfs extension:

```r
DBI::dbExecute(con, "SET httpfs_client_implementation = 'curl';")
DBI::dbExecute(con, "SET http_timeout = 120;")
DBI::dbExecute(con, "SET httpfs_connection_caching = true;")
```

`httpfs_client_implementation = 'curl'` switches DuckDB from its built-in
`httplib` implementation to libcurl, which has a different and in this case
more reliable code path for S3 range requests. The system `curl` binary was
already being used successfully elsewhere in this package (in `download_file`)
so the underlying library is known to work in this network environment.

`http_timeout = 120` gives each individual HTTP range request up to 120
seconds before timing out, up from the 30-second default. This is a backstop
for genuinely slow responses rather than a fix on its own.

`httpfs_connection_caching = true` enables connection pooling, so sequential
range requests to the same S3 host reuse an already-established TLS session.
Without this, each of the 100+ HTTP range requests across a full state
partition scan incurs a full TCP handshake and TLS negotiation, adding
hundreds of milliseconds of overhead per request.

### Why queries are still slower than they were in mid-2025

Even with the above settings applied, S3 queries via httpfs are noticeably
slower than they were roughly six months prior. There are several likely
contributing factors. DuckDB's httpfs extension has been updated repeatedly
across the v1.4 and v1.5 release series (bumped in v1.5.2 and v1.5.3 release
notes), and the default HTTP client implementation has changed in ways that
affect connection setup and range request behaviour. The BDC data releases
themselves have grown — D25 parquet files are larger than J24 files as FCC
adds more reported locations each cycle — which directly increases the amount
of data DuckDB must read per state partition. Finally, `get_frn_nbm_bl`
performs a full scan across all 57 state and territory partitions
(`s3://cori.data.fcc/nbm_block-{release}/*/*.parquet`) because FRN does not
map to a partition key, so every new row of data added to any partition adds
incremental cost to every call. The local-cache pattern used by `get_nbm_bl`
and `get_nbm_county` (syncing only the relevant state via `aws s3 sync` before
querying from disk) avoids this problem entirely and is the recommended
approach for repeated or latency-sensitive queries.

