---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cori.data.fcc

<!-- badges: start -->
<!-- badges: end -->

The goal of cori.data.fcc is to facilate the discovery, the download and the use of FCC's National Broadband Map [(NBM)](https://broadbandmap.fcc.gov/home) data.

## Installation

You can install the development version of cori.data.fcc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ruralinnovation/cori.data.fcc")
```

## Example

This is a basic example which shows some basic workflow:

```{r example-release}
library(cori.data.fcc)

release <- get_nbm_release() # get the available releases
release
```

You can also inspect what is available:

```{r example-available}
nbm <- get_nbm_available() # get what data is available
# if we are intrested in  "Fixed Broadband" / "Nationwide" / released "June 30, 2023"
nbm_filter <- nbm[which(nbm$release == "June 30, 2023" &
                        nbm$data_type == "Fixed Broadband" &
                        nbm$data_category == "Nationwide"), ]
rownames(nbm_filter) <- NULL


# or
nbm_dplyr_filter <- nbm |> dplyr::filter(release == "June 30, 2023" &
                                         data_type == "Fixed Broadband" &
                                         data_category == "Nationwide")
all.equal(nbm_filter, nbm_dplyr_filter)
head(nbm_filter)
```


The package also provide the list of Provider ID and FRN 

```{r fcc_provider}
str(fcc_provider)
```

## Inspiration

This package was imspired by https://github.com/bbcommons/bfm-explorer 