---
title: "National Broadband Map (NBM)"
output: rmarkdown::html_vignette
code_folding: hide
vignette: >
  %\VignetteIndexEntry{National Broadband Map (NBM)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(DT)
table_with_options <- function(x){DT::datatable(x, rownames = FALSE,
              extensions = 'Buttons',
                options = list(
                          dom = 'Blfrtip',
                          buttons = list('copy', 'print', list(
                            extend = 'collection',
                            buttons = c('csv', 'excel'),
                            text = 'Download')
                                    )
                          )
            )}
```

```{r setup}
library(cori.data.fcc)
```

# What is the National Broadband Map (NBM) data set?

## License and Attribution

The license can be found [here](https://broadbandmap.fcc.gov/about):

> Broadband availability data from the BDC, and data from the U.S. Census Bureau that are presented on this site, are offered free and not subject to copyright restriction. Data and content created by government employees within the scope of their employment are not subject to domestic copyright protection under 17 U.S.C. § 105. See, e.g., [U.S. Government Works](https://www.usa.gov/government-copyright).
>
> While not required, when using in your own work content, data, documentation, code, and related materials from fcc.gov or broadbandmap.fcc.gov, we ask that you provide proper attribution of the data. Examples include:
>
>    Source data: FCC Broadband Data Collection
>    Map layer based on FCC BDC
>
> CostQuest Associates, Inc. and its third-party licensors, as applicable, own all right, title, and interest, including all intellectual property rights, in and to the data for locations reflected in the Fabric (including the Location ID, latitude and longitude, address, unit count, and building type code for each location in the Fabric). CostQuest is granted certain rights to Fabric correction submissions for the purpose of correcting or otherwise modifying BDC Fabric data. Broadband service providers, governmental entities, and other third parties are able to license Fabric data, including any changes to Fabric data that have been made as a result of challenges, at no cost for purposes of their participation in the FCC's Broadband Data Collection.


## A Quick Introduction 

NBM was launched by the FCC in November 2022[^fcc_nbm_start] and follows [Form 477](https://ruralinnovation.github.io/cori.data.fcc/articles/f477.html). 

[^fcc_nbm_start]: [https://www.fcc.gov/news-events/notes/2022/11/18/new-broadband-maps-are-finally-here](https://www.fcc.gov/news-events/notes/2022/11/18/new-broadband-maps-are-finally-here)

Behind the National Broadband Map, there are **two** datasets (see @fig-broadbanddata, below). 
We use the "Broadband Availability" dataset that is derived from the "Fabric" locations dataset (developed by CostQuest). 
The locations are determined within the Fabric locations data. 

This dataset can be derived in multiple ways: by States or by Providers.  

At the state level, the data can be split between summaries and "raw data".
The summaries available are by geographies or by technologies (Fixed Broadband and Mobile Broadband).

For every state, you need to access the raw data by technology. 
In our work, we focused on Fixed Broadband Availability data. 

The NBM provides information about the scale of a "service" - a location covered by a provider and by a technology with a specific maximum speed.

This formatting approach is one of the big changes compared to Form 477. 
We moved from a Cesus-block scale to location-based scale (See @sec-BSL for a definition). 

Every location is characterized by:

- Who is providing those services (`frn`, `provider_id`, and `brand_name`)
- A description of each service (`technology`, `max_advertised_download_speed`, `max_advertised_upload_speed`, `low_latency`)
- Whether the location is residential, business or both
- Ways to localize the location (`state_abbr`, `block_geoid`, `h3_res8_id`)

In our ingestion, we did not keep the `h3_res8_id` property, but we added the 
date of the release and the timestamp provided in the 
filename (see `data-raw/NBM.R` to get every details).

The exact coordinates of every location is only part of the Fabric dataset. 
Within the Broadband Availability data, we can only link a record for a location 
to a Census Block (2020 vintage) or H3 hexagon.

!["What is on the national broadband map" Source: [https://www.fcc.gov/BroadbandData](https://www.fcc.gov/BroadbandData)](whats-on-the-national-broadband-map-113023-1.png){#fig-broadbanddata}

### What is a Broadband Service Location (BSL)? {#sec-BSL}

> A broadband serviceable location is defined as “a business or residential location in the United States at which fixed broadband Internet access service is, or can be, installed.” 
A residential BSL includes all residential structures, including structures that are (or contain) housing units or group quarters (as those terms are defined by the United States Census Bureau).  
A business BSL includes “all non-residential (business, government, non-profit, etc.) structures that are on property without residential locations and that would expect to demand Internet access service.” (source FCC[^fcc_bsl])

[^fcc_bsl]: ["The Fabric data"](https://help.bdc.fcc.gov/hc/en-us/articles/7412732399003-Fabric-FAQs)

### When is this data updated?

NBM has two big releases per year (June and December) and have versions every two weeks to take into account challenges[^challenges]. 
Sometimes their release can be faster (more than one per week) or slower.
The FCC did not (April 2024) provide a changelog between releases or versions (but the documentation has some of the major changes[^nbm_chnagelog]). 

[^challenges]: [https://www.fcc.gov/sites/default/files/bdc-challenge-overview.pdf](https://www.fcc.gov/sites/default/files/bdc-challenge-overview.pdf)

[^nbm_chnagelog]:See "Change Log" [https://us-fcc.app.box.com/v/bdc-data-downloads-output](https://us-fcc.app.box.com/v/bdc-data-downloads-output)


### What is the geographic coverage?

The Broadband Availability data covers all US States, Puerto Rico, and the US territories.  


# How does cori.data.fcc help me access NBM data? 

`cori.data.fcc` helps you access this dataset in 3 different ways: 

1. The package provides functions to list available data and download it 

2. We ingested all the Fixed Broadband Availability Data and are providing it 
in a s3 bucket (for more performant data loading!)

3. We ingested all Fixed Broadband Availability data and transformed all information
to be available at the Census block level.


### NBM Raw Data dictionary 

This dataset is called "nbm_raw" and its dictionary can be accessed with the function `get_fcc_dictionary`:

```{r nbm-data-dic}
table_with_options(get_fcc_dictionary("nbm_raw"))
```


### NBM Block Data Dictionary

This dataset is called "nbm_block"

```{r nbm-data-dic2}
table_with_options(get_fcc_dictionary("nbm_block"))
```


<!--
## What is unserved v.s. underseved?

Served, Unserved and Underseved are **overlapping** categories at the **location level**. They can be extended up to the "**area level**".

If all available internet services at a location have advertised (reported) maximum speeds that are below 25 Mbps downstream speed or below 3 Mbps upstream (25/3 to simplify), then that location is categorized as **unserved**. If a location has at least one service with maximum speeds that are equal to or above 25/3, but no service with maximum speeds that are equal to or above 100/20, it is categorized as **underserved**. If a location has at least one service with maximum speeds that are equal to or above 100/20, then that location is categorized as **served**.

Those definitions are recommended in the [FCC's Broadband Speed Benchmark](https://www.fcc.gov/document/fcc-increases-broadband-speed-benchmark) and can be adapted by every States[^pew_list].

[^pew_list]: Page 4 [https://www.pewtrusts.org/-/media/assets/2023/06/un--and-underserved-definitions-ta-memo-pdf.pdf](https://www.pewtrusts.org/-/media/assets/2023/06/un--and-underserved-definitions-ta-memo-pdf.pdf)

:::{.aside}
FCC could change those definitions and for example move the bar at 100/20: [https://www.fcc.gov/document/fcc-increases-broadband-speed-benchmark](https://www.fcc.gov/document/fcc-increases-broadband-speed-benchmark)
:::
-->




